Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-21 paper/sec-analysis.tex
push textual changes

It is also interesting to quantify how
the relative differences between
signal over background distributions are modified by the inclusion of PU.
%
Considering first of all the boosted category,
in Fig.~\ref{fig:signal-vs-back-boosted} we compare
various kinematic distributions for signal and background events,
with and without PU for the leading Higgs candidate: the invariant mass, the transverse
momentum distribution $p_T$,
     the 2--to--1 subjettiness ratio $\tau_{21}$, and 
     the $k_T$ splitting scale $\sqrt{d_{12}}$.
     %
      We verify that the relevant
      qualitative differences between signal
      and background distributions are maintained  in the presence of PU.
      %
      This is especially noticeable for the substructure variables, which
      exhibit a similar discrimination power both with and without
      PU.

@@

We can also perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
     with and without PU, for the invariant mass and the $p_T$ of the leading
     Higgs candidate.
     %
     Also in this
     case the PU-subtracted background distributions appear reasonably close
     to their no PU counterparts.

@@

To complete this discussion, it is illustrative to determine
which is the mass resolution obtained for the
reconstructed Higgs candidates in various cases.
%
In Table~\ref{tab:massresolution}
we indicate the shift of the invariant mass peak as compared
to the nominal Higgs mass, $\delta m_h$, as well as the
corresponding width of the distribution, $\sigma_{m_h}$,
obtained from fitting a Gaussian to the mass distributions
of both the leading and subleading Higgs candidates in
the resolved category.
        %
        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction, and the same with SK subtraction.
%
        We find a mass resolution of around 9 GeV in the case
        without PU, which worsens only slightly
        to around 11 GeV in the case of $\la n_{\rm PU}\ra=80$ PU
        with SK subtraction.
        %
        We also note that after subtraction, the peak of
        the invariant mass distributions of Higgs candidates
        coincides with the nominal values of $m_h$ within a few GeV.

>>>>

It is also interesting to quantify how
the relative differences between
signal over background distributions are modified by the inclusion of PU.
%
Considering the boosted category initially,
in Fig.~\ref{fig:signal-vs-back-boosted} we compare
various kinematic distributions for signal and background events,
with and without PU for the leading Higgs candidate: the invariant mass, the transverse
momentum distribution $p_T$,
     the 2--to--1 subjettiness ratio $\tau_{21}$, and 
     the $k_T$ splitting scale $\sqrt{d_{12}}$.
     %
      We verify that the relevant
      qualitative differences between signal
      and background distributions are maintained  in the presence of PU.
      %
      This is especially noticeable for the substructure variables, which
      exhibit a similar discriminatory power both with and without
      PU.

@@

We can also perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
     with and without PU, for the invariant mass and the $p_T$ of the leading
     Higgs candidate.
     %
%     Also in this
%     case
Again, the PU-subtracted background distributions appear reasonably close
     to their no PU counterparts.

@@

To complete this discussion, it is illustrative to determine
the mass resolution obtained for the
reconstructed Higgs candidates in the various cases.
%
In Table~\ref{tab:massresolution}
we indicate the shift of the invariant mass peak as compared
to the nominal Higgs mass, $\delta m_h$, %as well as the
and the corresponding width of the distribution, $\sigma_{m_h}$,
obtained from fitting a Gaussian to the mass distributions
of both the leading and subleading Higgs candidates in
the resolved category.
        %
        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction, and the same with SK subtraction.
%
        We find a mass resolution of around 9 GeV in the case
        without PU, which worsens only slightly
        to around 11 GeV in the case of $\la n_{\rm PU}\ra=80$ PU
        with SK subtraction.
        %
        We also note that after subtraction, the peak of
        the invariant mass distributions of Higgs candidates
        coincides with the nominal values of $m_h$ within a few GeV.

### 2015-12-21 paper/sec-conclusions.tex
Done with corrections
push textual changes

In this work we have presented a feasibility study for
 the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the High-Luminosity LHC with $\mathcal{L}=3$ ab$^{-1}$.
%
Our strategy is based on the combination of traditional
cut-based analysis with state-of-the-art multivariate techniques.
%
We take into account 
the most relevant backgrounds, in particular
the irreducible $4b$
and the reducible 
$2b2j$ and $4j$ QCD multijets.
%
We have illustrated how the $2b2j$ component leads to
a contribution comparable to that of the $4b$ process,
due to a combination of  parton shower effects, $b$-quark 
pair radiation, and selection requirements.
%
We have also demonstrated the robustness of our analysis strategy
under the addition of significant pileup.

@@

In this work we have considered only the SM production mechanism,
but many BSM scenarios predict deviations
in Higgs pair production, both at the level of total rates
and of
differential distributions.
%
In the absence of new explicit degrees of freedom,
deviations from the SM can be parametrized in
the EFT framework using higher-order
operators~\cite{Azatov:2015oxa,Goertz:2014qta}.
%
We therefore plan to study the constraints
on the coefficients of these effective
operators that can be obtained from measurements
of various kinematical distributions
in the $hh\to b\bar{b}b\bar{b}$ process.
%
Note that the higher rates of the $b\bar{b}b\bar{b}$ final state as compared to
other final states, such as
$b\bar{b}\gamma\gamma$, allow for a better constraint upon operators
that modify the high-energy behavior
of the theory, for instance,
it would become possible
to access the tail of the $m_{hh}$ distribution.

>>>>

In this work we have presented a feasibility study for
 the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the High-Luminosity LHC with $\mathcal{L}=3$ ab$^{-1}$.
%
Our strategy is based on the combination of traditional
cut-based analysis with state-of-the-art multivariate techniques.
%
We take into account 
all relevant backgrounds, in particular
the irreducible $4b$
and the reducible 
$2b2j$ and $4j$ QCD multijets.
%
We have illustrated how the $2b2j$ component leads to
a contribution comparable to that of the $4b$ process,
due to a combination of  parton shower effects, $b$-quark 
pair radiation, and selection requirements.
%
We have also demonstrated the robustness of our analysis strategy
under the addition of significant pileup.

@@

In this work we have considered only the SM production mechanism,
but many BSM scenarios predict deviations
in Higgs pair production, both at the level of total rates
and of
differential distributions.
%
In the absence of new explicit degrees of freedom,
deviations from the SM can be parametrized in
the EFT framework using higher-order
operators~\cite{Azatov:2015oxa,Goertz:2014qta}.
%
Therefore, we plan to study the constraints
on the coefficients of these effective
operators that can be obtained from measurements
of various kinematical distributions
in the $hh\to b\bar{b}b\bar{b}$ process.
%
Note that the higher rates of the $b\bar{b}b\bar{b}$ final state as compared to
other final states, such as
$b\bar{b}\gamma\gamma$, allow for a better constraint upon operators
that modify the high-energy behavior
of the theory, for instance,
it would become possible
to access the tail of the $m_{hh}$ distribution.

### 2015-12-21 paper/sec-mva.tex
Done with corrections
push textual changes

At the end of the cut-based analysis,
by combining the three event topologies,
we obtain a signal significance of $S/\sqrt{B}\simeq 1.8~(3.5)$
with all backgrounds (only QCD $4b$) taken into account.
%
We now show how this signal significance
 can be enhanced when the cut-based analysis
 is complemented by a multivariate analysis.
%
 Multivariate techniques are by now a mature tool
 in high-energy physics data analysis, opening
 new avenues for improving the performance
of many measurements and searches at high-energy colliders.
%
In particular, the classification of events into
signal and
background processes by means of MVAs is
commonly used in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.

In this section, first of all we present the specific MVA that we use,
based on feed-forward multi-layer neural networks.
%
We then introduce the input variables that are
used in the MVA, including the jet substructure
variables, and then present the signal significance obtained
by applying the MVA.
%
Then we assess the robustness of the MVA strategy in
the case of significant contamination from pileup.

@@

In this work, the ANN that we use has the following architecture.
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
which is different in the resolved, intermediate, and boosted categories.
%
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the ANN output.
%
In Fig.~\ref{fig:nnarch} we show an illustrative
example of a ANN used in this work, corresponding 
to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).

@@

From Table~\ref{table:cutflowMVA} we see that
after the application of the MVA, 
the signal significance in the boosted category increases
from 1.2 to 5.4, with $S/B$ increasing from $0.14\%$ to $3.4\%$,
with almost 800 signal events expected at the HL-LHC.
%
For the intermediate and resolved categories, $S/\sqrt{B}$
increases from 0.9 and 1.0 to 4.8 and 4.5, with
the signal over background ratio raising from
$0.12\%$ and $0.03\%$ to 6\% and 1\$, respectively.
%
The overall combined significance is thus $S\sqrt{B}\simeq 8$,
well above the threshold for discovery. However such a significance
is unrealistic given that the HL-LHC will be a high-PU environment,
which will affect the description of the various
kinematical distributions used as input to the MVA.
%
Therefore we shall now quantify the robustness of the
results summarized Table~\ref{fig:sb_mva}
in a realistic environment including the effects of PU.

@@

In Fig.~\ref{fig:nev2_PU}
we show the number of signal and background events that
are expected at the HL-LHC as a function of
$y_{\rm cut}$, as well as the corresponding ROC curve.
%
Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we observe
that the intermediate category is substantially worsened once PU effects
are accounted for due to a sizable
reduction in the number of signal
events that are now classified in this category.
%
This shows that the selection criteria
of the intermediate category are less
resilient against PU contamination,
as opposed to the resolved and boosted selections.

@@

In Table~\ref{table:cutflowMVA_fakes} we compare,
after the MVA is applied,
the 
number of background events  expected at the HL-LHC.
Both the total number, $N_{\rm ev}^{\rm tot}$,
and those from the  QCD $4b$ component
$N_{\rm ev}^{\rm 4b}$, for the analyses without and
with PU.
%
 We also quote the corresponding values of the signal 
    significance and the signal over background ratio.
    %
    Note that the MVA has been trained to the total background sample,
    though differences
    in the kinematic distributions of the $4b$ and $2b2j$ processes are small,
    see Fig.~\ref{fig:histoBack}.
    %
    The largest improvement from eliminating the contamination
    from light and charm jet mis-identification arises
    for the boosted and resolved categories.
%

>>>>

At the end of the cut-based analysis,
by combining the three event topologies,
we obtain a signal significance of $S/\sqrt{B}\simeq 1.8~(3.5)$
with all backgrounds (only QCD $4b$) considered.
%
This section describes how this signal significance
 can be enhanced when the cut-based analysis
 is complemented by a multivariate analysis.
%
 Multivariate techniques are a mature tool
 in high-energy physics data analysis, opening
 new avenues to improve the performance
of many measurements and searches at high-energy colliders.
%
In particular, the classification of events into
signal and
background processes by means of MVAs is
commonly used in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.

In this section, first we present the specific MVA that we use,
based on feed-forward multi-layer neural networks.
%
Then we introduce the input variables that are
used in the MVA, including the jet substructure
variables, and then present the signal significance obtained
by applying the MVA.
%
Then we assess the robustness of the MVA strategy in
the case of significant contamination from pileup.

@@

In this work, the ANN that we use has the following architecture.
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
which is different in the resolved, intermediate, and boosted categories.
%
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the ANN output.
%
In Fig.~\ref{fig:nnarch} we show an illustrative
example of an ANN used in this work, corresponding 
to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).

@@

From Table~\ref{table:cutflowMVA} we see that
after the application of the MVA, 
the signal significance in the boosted category increases
from 1.2 to 5.4, with $S/B$ increasing from $0.14\%$ to $3.4\%$,
with almost 800 signal events expected at the HL-LHC.
%
For the intermediate and resolved categories, $S/\sqrt{B}$
increases from 0.9 and 1.0 to 4.8 and 4.5, with
the signal over background ratio raising from
$0.12\%$ and $0.03\%$ to 6\% and 1\%, respectively.
%
The overall combined significance is thus $S\sqrt{B}\simeq 8$,
well above the threshold for discovery. However such a significance
is unrealistic given that the HL-LHC will be a high-PU environment,
which will affect the description of the various
kinematical distributions used as input to the MVA.
%
Therefore we shall now quantify the robustness of the
results summarized Table~\ref{fig:sb_mva}
in a realistic environment including the effects of PU.

@@

In Fig.~\ref{fig:nev2_PU}
we show the number of signal and background events that
are expected at the HL-LHC as a function of
$y_{\rm cut}$, as well as the corresponding ROC curve.
%
Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we observe
that the intermediate category is substantially worsened once PU effects
are accounted for due to a sizable
reduction in the number of signal
events that are now classified in this category.
%
This shows that the selection criteria
of the intermediate category are less
resilient against PU contamination,
in contrast to the resolved and boosted selections.

@@

In Table~\ref{table:cutflowMVA_fakes} we compare,
number of background events  expected at the HL-LHC, after the MVA is applied.
Both the total number, $N_{\rm ev}^{\rm tot}$,
and those from the  QCD $4b$ component
$N_{\rm ev}^{\rm 4b}$, for the analyses without and
with PU.
%
 We also quote the corresponding values of the signal 
    significance and the signal over background ratio.
    %
    Note that the MVA has been trained to the total background sample,
    though differences
    in the kinematic distributions of the $4b$ and $2b2j$ processes are small,
    see Fig.~\ref{fig:histoBack}.
    %
    The largest improvement from eliminating the contamination
    from light and charm jet mis-identification arises
    for the boosted and resolved categories.
%

### 2015-12-21 paper/sec-results.tex
Done with corrections
push textual changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section{Results of the cut-based analysis}

@@

In this section we present the results of the 
cut-based analysis described in the previous section, and provide 
cut-flows for the different analysis steps.
%
We
compare our results with other recent studies,
and assess how the signal significance
is affected if only the $4b$ component of the
QCD multi-jet background is taken into account.
%
Here we present the results in an environment without pile-up,
followed in the next section by the corresponding analysis including PU.

@@

    In Table~\ref{tab:cutflow_noPU_1} we collect
    the values for signal and background cross-sections
    for different steps of the cut-flow.
    %
    Results are divided into the resolved, intermediate and boosted categories,
    and are inclusive up to the C2 level, where exclusivity is imposed.
    %
In Table~\ref{tab:cutflow_noPU_1} we also  provide the signal over
      background ratio, $S/B$, and the signal
      significance, $S/\sqrt{B}$, corresponding to an integrated
      luminosity of $\mathcal{L}=3$ ab$^{-1}$.
      %
      These are provided both taking into account all the background components and only
      the $4b$ QCD background.
        %
      We find that after $b$-tagging, the  $2b2j$ component is
      of the same order of magnitude as the $4b$ component in all categories.
      %
      This implies that the signal significance at the end of the cut-based
      analysis is degraded due to the contribution
      of light and charm jets being mis-identified as $b$-jets.

@@

 Also from Table~\ref{tab:cutflow_noPU_1}, we
 can compare the interplay
 between the reducible and irreducible components of the
 QCD backgrounds.
 %
 In all cases, the $4b$ and $2b2j$ have comparable
 magnitudes within the uncertainties from missing higher-order
 corrections.
 %
 On the other hand, the $4j$ component
is always smaller by at least
 one order of magnitude.
 %
  So while the $4j$ component can be safely
 neglected, the inclusion of the
 $2b2j$ component is essential to robustly assess the feasibility
 of measuring Higgs pairs in this final state,
 especially
 in the boosted category.
 %
 This has the important
 consequence that a promising avenue to improve the prospects
 of this measurement would be to reduce, as much as possible,
 the light and charm jet mis-identification rate.

@@

We can make these statements more quantitative in the following way.
%
To first approximation, and neglecting the contribution from
charm mis-identification,
the
overall efficiency of the $b$-tagging requirements in the resolved category will be
given by the following expression:
\be
\label{btaggingeff}
{\rm EFF}_{\rm b-tag}\simeq \sum_{j=0}^{4}n^{\rm (b-jet)}_j\cdot f_b^{j}\cdot f_l^{4-j} \, ,
\ee
with $n^{\rm (b-jet)}_j$ being the fraction of events satisfying all the selection
requirements,
where $j$ jets out of the leading four jets of the event
contain $b$ quarks (with $p_T^b\ge 15$
GeV).
%
Similar expressions can be derived for
the boosted and intermediate categories.
%
The naive expectation is that all events in the $4b$ sample have $n^{\rm (b-jet)}_4\simeq 1$
and $n^{\rm (b-jet)}_j\simeq 0$ for $j\ne 4$, while the events in the $2b2j$ sample
should have $n^{\rm (b-jet)}_2\simeq 1$ and zero otherwise.
%
This leads to a ratio of overall $b$-tagging selection efficiencies
\be
\label{eq:naive}
\frac{ {\rm EFF}_{\rm b-tag} \lc 2b2j \rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}
  \simeq
 \lp \frac{f_l}{f_b}\rp^2 \simeq 1.5\cdot 10^{-4} \, .
\ee
However, after the parton shower the above approach is no longer accurate.
%
First of all, we will have a non-negligible fraction $n^{\rm (b-jet)}_j$
with $j=3,4$ also in the $2b2j$ sample, due to $b$-quark pair radiation
during the shower.
%
Secondly, not all events in the $4b$ sample will lead to four small-$R$ $b$-jets,
due to a combination of selection cuts and
parton shower effects.
%

@@

In Table~\ref{tab:btaggingcheck} we collect
the values of $n^{\rm (b-jet)}_j$ for the signal and the three QCD background samples.
%
We find that rather than the estimate Eq.~(\ref{eq:naive}),
the correct ratio of $b$-tagging selection efficiencies is instead
\be
\frac{{\rm EFF}_{\rm b-tag} \lc 2b2j\rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}=
  \frac{0.04\%}{8.4\%} \simeq 5\cdot 10^{-3} \, .
  \ee
  This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
    %
    This explains why the $2b2j$ contribution cannot be neglected as compared
    to the irreducible $4b$ component of the QCD background.
    %
    A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
    that, on the other hand, the $4j$ component of the background can typically
    be safely neglected.

>>>>

\section{Results of the cut-based analysis}

@@

In this section we present the results of the 
cut-based analysis described in the previous section, and provide 
cut-flows for the different analysis steps.
%
We
compare our results with other recent studies,
and assess how the signal significance
is affected if only the $4b$ component of the
QCD multi-jet background is taken into account.
%
%Here we present the results in an environment without pile-up,
%followed in the next section by the corresponding analysis including PU.
This section presents the results in an environment without significant pile-up; the following one details those obtained includin PU.

@@

    In Table~\ref{tab:cutflow_noPU_1} we collect
    the values for signal and background cross-sections
    at different steps of the cut-flow.
    %
    Results are divided into the resolved, intermediate and boosted categories,
    and are inclusive up to the C2 level, where exclusivity is imposed.
    %
In Table~\ref{tab:cutflow_noPU_1} we also  provide the signal over
      background ratio, $S/B$, and the signal
      significance, $S/\sqrt{B}$, corresponding to an integrated
      luminosity of $\mathcal{L}=3$ ab$^{-1}$.
      %
      These are provided both taking into account all the background components and only
      the $4b$ QCD background.
        %
      We find that after $b$-tagging, the  $2b2j$ component is
      of the same order of magnitude as the $4b$ component in all categories.
      %
      This implies that the signal significance at the end of the cut-based
      analysis is degraded due to the contribution
      of light and charm jets being mis-identified as $b$-jets.

@@

 Also from Table~\ref{tab:cutflow_noPU_1}, we
 can compare the interplay
 between the reducible and irreducible components of the
 QCD backgrounds.
 %
 In all cases, the $4b$ and $2b2j$ have comparable
 magnitudes within the uncertainties from missing higher-order
 corrections.
 %
 On the other hand, the $4j$ component
is always smaller by at least
 one order of magnitude.
 %
  So while the $4j$ component can be safely
 neglected, the inclusion of the
 $2b2j$ component is essential to assess the feasibility
 of measuring Higgs pairs in this final state robustly,
 especially
 in the boosted category.
 %
 This has the important
 consequence that a promising avenue to improve the prospects
 of this measurement would be to reduce, as much as possible,
 the light and charm jet mis-identification rate.

@@

We can make these statements more quantitative in the following way.
%
To first approximation, neglecting the contribution from
charm mis-identification,
the
overall efficiency of the $b$-tagging requirements in the resolved category will be
given by the following expression:
\be
\label{btaggingeff}
{\rm EFF}_{\rm b-tag}\simeq \sum_{j=0}^{4}n^{\rm (b-jet)}_j\cdot f_b^{j}\cdot f_l^{4-j} \, ,
\ee
with $n^{\rm (b-jet)}_j$ being the fraction of events satisfying all the selection
requirements,
where $j$ jets out of the leading four jets of the event
contain $b$ quarks (with $p_T^b\ge 15$
GeV).
%
Similar expressions can be derived for
the boosted and intermediate categories.
%
The naive expectation is that all events in the $4b$ sample have $n^{\rm (b-jet)}_4\simeq 1$
and $n^{\rm (b-jet)}_j\simeq 0$ for $j\ne 4$, while the events in the $2b2j$ sample
should have $n^{\rm (b-jet)}_2\simeq 1$ and zero otherwise.
%
This leads to a ratio of overall $b$-tagging selection efficiencies
\be
\label{eq:naive}
\frac{ {\rm EFF}_{\rm b-tag} \lc 2b2j \rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}
  \simeq
 \lp \frac{f_l}{f_b}\rp^2 \simeq 1.5\cdot 10^{-4} \, .
\ee
However, after the parton shower the above approach is no longer accurate.
%
First of all, we will have a non-negligible fraction $n^{\rm (b-jet)}_j$
with $j=3,4$ also in the $2b2j$ sample, due to $b$-quark pair radiation
during the shower.
%
Secondly, not all events in the $4b$ sample will lead to four small-$R$ $b$-jets,
due to a combination of selection cuts and
parton shower effects.
%

@@

In Table~\ref{tab:btaggingcheck} we collect
the values of $n^{\rm (b-jet)}_j$ for the signal and the three QCD background samples.
%
We find that rather than the estimate Eq.~(\ref{eq:naive}),
the correct ratio of $b$-tagging selection efficiencies is instead
\be
\frac{{\rm EFF}_{\rm b-tag} \lc 2b2j\rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}=
  \frac{0.04\%}{8.4\%} \simeq 5\cdot 10^{-3} \, .
  \ee
  This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
    %
    This explains why the $2b2j$ contribution cannot be neglected as compared
    to the irreducible $4b$ component of the QCD background.
    %
    A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
    that, on the other hand, the $4j$ component of the background is negligible and be neglected. % can typically
%    be safely neglected.
